Python as a machine learning language: experiences from the scikit-learn project

### 2013-06-11 paper.tex
start comparison section

>>>>

Recent years have witnessed a rising interest in machine learning and data mining
with applications in many fields.
With this rise comes a host of machine learning packages
(both open source and proprietary) with which \sklearn competes.

% XXX Is the Julia comparison fair?
% The goal of that language seems to be a bit different:
% to provide a compiler to implement numeric algorithms without vectorized idioms,
% maybe more like Cython than Python...
In comparison to specialized languages for numeric and statistical programming
such as \textsc{matlab}, R \citep{trancon2012r} and Julia \citep{bezanson2012julia},
the use of Python as a host language has the distinct advantage
that it is a mature, \textit{general purpose} language:
it has strong language and standard library support for such tasks as
string handling/text processing, interprocess communication, networking
and many of the other tasks that many machine learning programs
(whether academic or commercial)
will have to perform ``on the side''.
In addition, third-party libraries are available for virtually any task
that modern computer programs routinely perform.
